Privacy-Preserving Localization Using Private Linear-Combination Aggregation

### 2021-05-27 main.tex
Pseudocode section draft Moved leakage section back to being after the pseudocode section

\section{Privacy-Preserving Localization} \label{sec:priv_localization}
To produce an estimate of the state $\vec{x}_k$ such that communication between $n$ range sensors and the navigator is reducible to the linear-combination aggregation protocol, we make use of an algebraic reformulation of the Extended Kalman Filter (EKF), the Extended Information Filter (EIF) \cite{maybeckStochasticModelsEstimation1982}, which reduces the filter update step to a single summation. The EIF update step requires the predicted state estimate $\vec{x}_{k|k-1}$ and estimate covariance $\mat{P}_{k|k-1}$ in the information vector and matrix forms
\begin{equation}
    \vec{y}_{k|k-1} = \mat{P}_{k|k-1}^{-1}\vec{x}_{k|k-1} \quad\textrm{and}\quad \mat{Y}_{k|k-1} = \mat{P}_{k|k-1}^{-1}\,,
\end{equation}
respectively. In this form, the update equations for $n$ sensor measurements at time $k$, given process and measurement models \eqref{eqn:system_model} and \eqref{eqn:measurement_model}, are given by
\begin{equation}
    \begin{split}
        &\vec{y}_{k|k} = \vec{y}_{k|k-1} + \\
        &\quad \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i (z_{k,i} - h_i(\vec{x}_{k|k-1}) + \mat{H}_{k,i}\vec{x}_{k|k-1})
    \end{split} \label{eqn:eif_info_vec_update}
\end{equation}
and
\begin{equation}
    \mat{Y}_{k|k} = \mat{Y}_{k|k-1} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i \mat{H}_{k,i}\,, \label{eqn:eif_info_mat_update}
\end{equation}
with Jacobians
\begin{equation}
    \mat{H}_{k,i} = \left.\frac{\partial h_i}{\partial \vec{x}}\right|_{\rvec{x}_{k|k-1}} \label{eqn:measurement_jacobian}
\end{equation}
for sensors $1 \leq i \leq n$. The filter's prediction step can be computed by converting information vector $\vec{y}_{k|k}$ and matrix $\mat{Y}_{k|k}$ back to state estimate and covariance 
\begin{equation}
    \vec{x}_{k|k} = \mat{Y}_{k|k}^{-1}\vec{y}_{k|k} \quad\textrm{and}\quad \mat{P}_{k|k} = \mat{Y}_{k|k}^{-1}\,,
\end{equation}
before using the normal EKF prediction equations
\begin{equation}
    \vec{x}_{k+1|k} = \vec{f}(\vec{x}_{k|k}) \quad\textrm{and}\quad \mat{P}_{k+1|k} = \mat{F}_k\mat{P}_{k|k}\mat{F}_k^\top + \mat{Q}_k\,,
\end{equation}
with Jacobian
\begin{equation}
    \mat{F}_{k} = \left.\frac{\partial \vec{f}}{\partial \vec{x}}\right|_{\vec{x}_{k|k}}\,. \label{eqn:jacobian_f}
\end{equation}

@@

The approximation of $z'_{k,i}$ and its variance $\mathsf{Var}[v'_{k,i}]$ from the original measurements $z_{k,i}$ are complicated by the noise term $v_{k,i} \sim \mathcal{N}(0, r_i)$ in \eqref{eqn:measurement_model}. Squaring the original range measurements produces
\begin{equation}
    \begin{split}
        z_{k,i}^2 &= (h_i(\vec{x}_k) + v_{k,i})^2 \\
        &= h'_i(\vec{x}_k) + 2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2\,,
    \end{split}
\end{equation}
with a new noise term $2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2$, now dependent on the measurement function $h_i$, and no longer zero-mean or Gaussian. We can compute the mean of this new noise term (a function of the Gaussian term $v_{k,i}$) as
\begin{equation}
    \mathsf{E}[2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2] = r_i\, \label{eqn:modified_noise_mean}
\end{equation}
and mean-adjust modified measurements as
\begin{equation} \label{eqn:modified_measurement}
    \begin{split}
        z'_{k,i} &= z_{k,i}^2 - r_i \\
        &= h_i(\vec{x}_k)^2 + 2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2 - r_i \\
        &= h'_i(\vec{x}_k) + v'_{k,i}\,,
    \end{split}
\end{equation}
with now zero-mean noise $v'_{k,i} = 2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2 - r_i$. The noise in this case (again a function of Gaussian term $v_{k,i}$) has variance 
\begin{equation}
    \mathsf{Var}[v'_{k,i}] = 4h_i(\vec{x}_k)^2r_i + 2r_i^2
\end{equation}
and is also dependent on $h_i(\vec{x}_k)$. To use the modified measurement \eqref{eqn:modified_measurement} with the EIF, we require an estimate for $\mathsf{Var}[v'_{k,i}]$ at the sensor as well. Additionally, a conservative estimate (\textit{i.e.}, a larger variance resulting in less confidence in measurements) is desirable to reduce filter divergence. The naive approach, replacing $h_i(\vec{x}_k)$ with $z_{k,i}$, only provides a conservative estimate when
\begin{equation}
    \begin{split}
        &z_{k,i} > h_i(\vec{x}_k) \\
        \implies &v_{k,i} > 0\,,
    \end{split}
\end{equation}
which cannot be guaranteed. Instead, we provide a conservative estimate with $95\%$ confidence due to the Gaussianity of $v_{k,i}$, by adjusting the replacement term $z_{k,i}$ by two of its standard deviations $\sqrt{r_i}$. The modified measurement's variance at time $k$ is therefore conservatively approximated by
\begin{equation}
    \begin{split}
        r_{k, i} &= 4(z_{k,i} + 2\sqrt{r_i})^2r_i + 2r_i^2 \\
        &\gtrapprox \Var{v'_{k,i}}
    \end{split}\,. \label{eqn:modified_measurement_variance_estimate}
\end{equation}
for each sensor $i$.

@@

@@

\subsection{Pseudocode} \label{subsec:pseudocode}

Due to the complexity
several levels of computations
we summarise the privacy-preserving localisation filter in this section

In this section, we piece together our LCAO secure encryption scheme in Section  with the modified measurement model in Sections  and  and define our privacy-preserving localization algorithm.

The privacy-preserving localization filter can be described by the following steps.
\begin{LaTeXdescription}
    \item[Setup] The $\mathsf{Setup}$ algorithm from Section  is executed by a trusted third party, $N$ and $H$ are made known to the navigator and all sensors, and the navigator and sensor secret keys, $sk_0=\lambda=\mathsf{lcm}(p-1, q-1)$ and $sk_i$, $1 \leq i \leq n$ respectively, are distributed accordingly. Additionally, we assume that fractional precision $\phi$ from Section \ref{subsec:encoding} is also a public parameter and made known to the navigator and sensors. We will thus simplify the encoding notation $\mathsf{E}_{N,\phi,d}(\cdot)$ to $\mathsf{E}_{d}(\cdot)$.

    \item[Prediction] The navigator computes the typical EKF prediction equations before encrypting state variables and broadcasting to sensors. This is given by Algorithm \ref{alg:nav_prediction}.

    \item[Measurement] Sensors modify their measurements before homomorphically computing measurement vectors and matrices $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$, encrypting them for aggregation, and sending them back to the navigator. Care must be taken when encoding during homomorphic operations to ensure fractional factor $d$ satisfies \eqref{eqn:encoding_homomorphic_add}, in particular when using the property from Remark \ref{rem:lcao_implicit_weight}. This is described by Algorithm \ref{alg:measurement_info}.

    \item[Update] The navigator aggregates measurement vectors and matrices before decrypting them. The typical EIF update equations can then be computed. This is shown in Algorithm \ref{alg:nav_update}.
\end{LaTeXdescription}

\begin{algorithm}[htbp]
\caption{Navigator Prediction}\label{alg:nav_prediction}
\begin{algorithmic}[1]
    \Procedure{Prediction}{$\rvec{x}_{k-1|k-1}$, $\mat{P}_{k-1|k-1}$, $\vec{f}$, $\mat{Q}$, $N$}

    \State Compute $\mat{F}_k$ by 
    \State $\rvec{x}_{k|k-1} \gets \vec{f}(\rvec{x}_{k-1|k-1})$
    \State $\mat{P}_{k|k-1} \gets \mat{F}_k\mat{P}_{k-1|k-1}\mat{F}_k^\top + \mat{Q}$

    \State Compute $\mathsf{E}_{0}(\rv{x}^3_{k|k-1})$ by \eqref{eqn:encode}
    \State Compute $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^3_{k|k-1}))$ by \eqref{eqn:our_scheme_encrypt}
    \State Broadcast $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^3_{k|k-1}))$ to sensors
    \For{Remaining weights in \eqref{eqn:weights_to_broadcast}} 
        \State Broadcast weight in the form above
    \EndFor

    \State \Return $\rvec{x}_{k|k-1}, \mat{P}_{k|k-1}$
    \EndProcedure
\end{algorithmic}
\end{algorithm}

    \State Measure $\rv{z}_{k,i}$
    \State Compute $\rv{z}_{k,i}'$ by \eqref{eqn:modified_measurement}
    \State Compute $\rv{r}_{k, i}$ by \eqref{eqn:modified_measurement_variance_estimate}

    \State Recieve $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^3_{k|k-1}))$
    \For{Remaining weights in \eqref{eqn:weights_to_broadcast}}
        \State Recieve weight in the form above
    \EndFor

    \State Let $\alpha_{v}^{(i)}$ represent an encryption of element $v$ in $\rvec{i}'_{k,i}$ from \eqref{eqn:hrz_linear_comb}
    \State $\alpha_{1}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^3_{k|k-1}))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_{k|k-1}\rv{y}^2_{k|k-1}))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^2_{k|k-1}))^{\mathsf{E}_{0}(-\rv{r}_{k, i}^{-1}s_{x,i})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{y}^2_{k|k-1}))^{\mathsf{E}_{0}(-2\rv{r}_{k, i}^{-1}s_{x,i})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_{k|k-1}))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1}\rv{z}_{k,i}')}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_{k|k-1}))^{\mathsf{E}_{0}(-2\rv{r}_{k, i}^{-1}s_{x,i}^2)}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_{k|k-1}))^{\mathsf{E}_{0}(-2\rv{r}_{k, i}^{-1}s_{y,i}^2)}\cdot$\par
    \ $(N+1)^{\mathsf{E}_{1}(2\rv{r}_{k, i}^{-1}s_{x,i}^3)}
    (N+1)^{\mathsf{E}_{1}(2\rv{r}_{k, i}^{-1}s_{x,i}s_{y,i}^2)}\cdot$\par
    \ $(N+1)^{\mathsf{E}_{1}(-2\rv{r}_{k, i}^{-1}s_{x,i}\rv{z}_{k,i}')}
    H(k\mathbin\|1\mathbin\|1\mathbin\|0)\pmod{N^2}$
    \State Compute $\alpha_{2}^{(i)}$ using \eqref{eqn:hrz_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and Remark \ref{rem:lcao_implicit_weight} in the form above
    \For{$v \gets 1$ to $2$}
        \State Send $\alpha_{v}^{(i)}$ to the navigator
    \EndFor

    \State Let $\beta_{vw}^{(i)}$ represent an encryption of element $(v,w)$ in $\mat{I}'_{k,i}$ from \eqref{eqn:hrh_linear_comb}
    \State $\beta_{11}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^2_{k|k-1}))^{\mathsf{E}_{0}(4\rv{r}_{k, i}^{-1})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_{k|k-1}))^{\mathsf{E}_{0}(-8\rv{r}_{k, i}^{-1}s_{x,i})}\cdot$\par
    \ $(N+1)^{\mathsf{E}_{1}(4\rv{r}_{k, i}^{-1}s_{x,i}^2)}\cdot$\par
    \ $H(k\mathbin\|1\mathbin\|1\mathbin\|1)\pmod{N^2}$
    \State Compute remaining $\beta_{vw}^{(i)}$ using \eqref{eqn:hrh_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and Remark \ref{rem:lcao_implicit_weight} in the form above
    \For{$v \gets 1$ to $2$}
        \For{$w \gets 1$ to $2$} 
            \State Send $\beta_{vw}^{(i)}$ to the navigator
        \EndFor
    \EndFor
    \EndProcedure
\end{algorithmic}
\end{algorithm}

\begin{algorithm}[htbp]
\caption{Navigator Update}\label{alg:nav_update}
\begin{algorithmic}[1]
    \Procedure{Update}{$\rvec{x}_{k|k-1}$, $\mat{P}_{k|k-1}$, $N$, $\lambda$}

    \State Let $\alpha_{v}$ represent an encryption of element $v$ in $\sum_{i=1}^n\rvec{i}'_{k,i}$
    \For{$v \gets 1$ to $2$}
        \State $\alpha_{v} \gets \prod_{i=1}^n\alpha_{v}^{(i)}$
        \State Compute $\mathcal{D}_{sk_0}(\alpha_{v})$ with $\lambda$ by \eqref{eqn:our_scheme_decrypt}
        \State Compute $\mathsf{E}^{-1}_{1}(\mathcal{D}_{sk_0}(\alpha_{v}))$ by \eqref{eqn:decode}
    \EndFor
    \State Construct $\sum_{i=1}^n\rvec{i}'_{k,i}$ from decoded decryptions above

    \State $\rvec{y}_{k|k} \gets \mat{P}_{k|k-1}^{-1}\rvec{x}_{k|k-1} + \sum_{i=1}^n\rvec{i}'_{k,i}$
    \State $\mat{Y}_{k|k} \gets \mat{P}_{k|k-1}^{-1} + \sum_{i=1}^n\mat{I}'_{k,i}$
    \State $\rvec{x}_{k|k} \gets \mat{Y}_{k|k}^{-1}\rvec{y}_{k|k}$
    \State $\mat{P}_{k|k} \gets \mat{Y}_{k|k}^{-1}$
    \State \Return $\rvec{x}_{k|k}, \mat{P}_{k|k}$
    \EndProcedure
\end{algorithmic}
\end{algorithm}

Algorithms \ref{alg:nav_prediction}, \ref{alg:measurement_info} and \ref{alg:nav_update} have been summarized graphically in Figure \ref{fig:alg_steps}, where encryptions and encodings of vectors and matrices have been denoted with $\mathcal{E}_{pk_0,sk_i}(\cdot)$ and $\mathsf{E}_d(\cdot)$ for brevity, and represent element-wise operations with the same parameters.

\begin{figure}[htbp]
\centering
\vspace{\baselineskip}
\begin{tikzpicture}[font=\footnotesize,scale=0.95]
    % Prediction
    \draw [gray] (0,2) rectangle (6.5,8);
    \node at (3.25,7.5) {\small 1. Prediction};

    % Navigator
    \fill  [blue!40] (2,7) rectangle (4.5,5.5);
    \pic[xscale=0.22,yscale=0.3] at (3.25,6.6725) {plane};
    \node at (3.25,5.875) {$\rvec{x}_{k|k-1}$, $\mat{P}_{k|k-1}$};

    \fill [lightgray]  (0.25,5) rectangle (6.25,4);
    \node at (3.25,4.5) {$\langle\mathcal{E}_{pk_0}(\mathsf{E}_0(\rv{\omega})) \,|\, \rv{\omega} \!\in\! \{\rv{x}^3_{k|k-1}, \rv{y}^3_{k|k-1}, \dots\}\rangle$};

    \node at (1.25,-3.125) {$\rv{z}'_{k,1}$, $\rv{r}_{k,1}$};
    \node at (5.25,-3.125) {$\rv{z}'_{k,n}$, $\rv{r}_{k,n}$};

>>>>

\section{Privacy-Preserving Localization} \label{sec:priv_localization}
To produce an estimate of the state $\vec{x}_k$ such that communication between $n$ range sensors and the navigator is reducible to the linear-combination aggregation protocol, we make use of an algebraic reformulation of the Extended Kalman Filter (EKF), the Extended Information Filter (EIF) \cite{maybeckStochasticModelsEstimation1982}, which reduces the filter update step to a single summation. The EIF update step requires the predicted state estimate $\vec{x}_{k|k-1}$ and estimate covariance $\mat{P}_{k|k-1}$ in the information vector and matrix forms
\begin{equation}
    \vec{y}_{k|k-1} = \mat{P}_{k|k-1}^{-1}\vec{x}_{k|k-1} \quad\textrm{and}\quad \mat{Y}_{k|k-1} = \mat{P}_{k|k-1}^{-1}\,,
\end{equation}
respectively. In this form, the update equations for $n$ sensor measurements at time $k$, given process and measurement models \eqref{eqn:system_model} and \eqref{eqn:measurement_model}, are given by
\begin{equation}
    \begin{split}
        &\vec{y}_{k|k} = \vec{y}_{k|k-1} + \\
        &\quad \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i (z_{k,i} - h_i(\vec{x}_{k|k-1}) + \mat{H}_{k,i}\vec{x}_{k|k-1})
    \end{split} \label{eqn:eif_info_vec_update}
\end{equation}
and
\begin{equation}
    \mat{Y}_{k|k} = \mat{Y}_{k|k-1} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i \mat{H}_{k,i}\,, \label{eqn:eif_info_mat_update}
\end{equation}
with Jacobians
\begin{equation}
    \mat{H}_{k,i} = \left.\frac{\partial h_i}{\partial \vec{x}}\right|_{\rvec{x}_{k|k-1}} \label{eqn:measurement_jacobian}
\end{equation}
for sensors $1 \leq i \leq n$. The filter's prediction step can be computed by converting information vector $\vec{y}_{k|k}$ and matrix $\mat{Y}_{k|k}$ back to state estimate and covariance 
\begin{equation}
    \vec{x}_{k|k} = \mat{Y}_{k|k}^{-1}\vec{y}_{k|k} \quad\textrm{and}\quad \mat{P}_{k|k} = \mat{Y}_{k|k}^{-1}\,,
\end{equation}
before using the normal EKF prediction equations
\begin{equation}
    \vec{x}_{k+1|k} = \vec{f}(\vec{x}_{k|k}) \quad\textrm{and}\quad \mat{P}_{k+1|k} = \mat{F}_k\mat{P}_{k|k}\mat{F}_k^\top + \mat{Q}_k\,,
\end{equation} \label{eqn:ekf_prediction}
with Jacobian
\begin{equation}
    \mat{F}_{k} = \left.\frac{\partial \vec{f}}{\partial \vec{x}}\right|_{\vec{x}_{k|k}}\,. \label{eqn:jacobian_f}
\end{equation}

@@

The approximation of $z'_{k,i}$ and its variance $\mathsf{Var}[v'_{k,i}]$ from the original measurements $z_{k,i}$ are complicated by the noise term $v_{k,i} \sim \mathcal{N}(0, r_i)$ in \eqref{eqn:measurement_model}. Squaring the original range measurements produces
\begin{equation}
    \begin{split}
        z_{k,i}^2 &= (h_i(\vec{x}_k) + v_{k,i})^2 \\
        &= h'_i(\vec{x}_k) + 2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2\,,
    \end{split}
\end{equation}
with a new noise term $2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2$, now dependent on the measurement function $h_i$, and no longer zero-mean or Gaussian. We can compute the mean of this new noise term (a function of the Gaussian term $v_{k,i}$) as
\begin{equation}
    \mathsf{E}[2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2] = r_i\, \label{eqn:modified_noise_mean}
\end{equation}
and mean-adjust modified measurements as
\begin{equation}
    \begin{split}
        z'_{k,i} &= z_{k,i}^2 - r_i \\
        &= h_i(\vec{x}_k)^2 + 2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2 - r_i \\
        &= h'_i(\vec{x}_k) + v'_{k,i}\,,
    \end{split} \label{eqn:modified_measurement}
\end{equation}
with now zero-mean noise $v'_{k,i} = 2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2 - r_i$. The noise in this case (again a function of Gaussian term $v_{k,i}$) has variance 
\begin{equation}
    \mathsf{Var}[v'_{k,i}] = 4h_i(\vec{x}_k)^2r_i + 2r_i^2
\end{equation}
and is also dependent on $h_i(\vec{x}_k)$. To use the modified measurement \eqref{eqn:modified_measurement} with the EIF, we require an estimate for $\mathsf{Var}[v'_{k,i}]$ at the sensor as well. Additionally, a conservative estimate (\textit{i.e.}, a larger variance resulting in less confidence in measurements) is desirable to reduce filter divergence. The naive approach, replacing $h_i(\vec{x}_k)$ with $z_{k,i}$, only provides a conservative estimate when
\begin{equation}
    \begin{split}
        &z_{k,i} > h_i(\vec{x}_k) \\
        \implies &v_{k,i} > 0\,,
    \end{split}
\end{equation}
which cannot be guaranteed. Instead, we provide a conservative estimate with $95\%$ confidence due to the Gaussianity of $v_{k,i}$, by adjusting the replacement term $z_{k,i}$ by two of its standard deviations $\sqrt{r_i}$. The modified measurement's variance at time $k$ is therefore conservatively approximated by
\begin{equation}
    \begin{split}
        r_{k, i} &= 4(z_{k,i} + 2\sqrt{r_i})^2r_i + 2r_i^2 \\
        &\gtrapprox \Var{v'_{k,i}}
    \end{split}\,. \label{eqn:modified_measurement_variance_estimate}
\end{equation}
for each sensor $i$.

@@

\subsection{Pseudocode} \label{subsec:pseudocode}
Measurement modification, real number encoding and linear combination aggregation are all required to compute the modified EIF from the previous section in a privacy-preserving manner. In this section, we summarise this entire localisation process and give the pseudocode for its execution. For brevity, we will assume $\phi$ and $M=N$ from section \ref{subsec:encoding} to be public information, and simplify the encoding notation $\mathsf{E}_{N,\phi,d}(\cdot)$ to $\mathsf{E}_{d}(\cdot)$. The privacy-preserving localization filter consists of the following steps.
\begin{LaTeXdescription}
    \item[Setup] Run only once, the $\mathsf{Setup}$ algorithm from section \ref{sec:lcao_scheme} is run by a trusted third party, $N$ and $H$ are made public, and the navigator and sensor secret keys, $sk_0=\lambda=\mathsf{lcm}(p-1, q-1)$ and $sk_i$, $1 \leq i \leq n$, are distributed accordingly.

    \item[Prediction] At each timestep $k$, the navigator computes the typical EKF prediction equations \eqref{eqn:ekf_prediction} before encrypting weights \eqref{eqn:weights_to_broadcast} with algorithm $\mathsf{Enc}$ and broadcasting them to the sensors. This is given by algorithm \ref{alg:nav_prediction}.

    \item[Measurement] At each timestep $k$, sensors modify their measurements with \eqref{eqn:modified_measurement} and \eqref{eqn:modified_measurement_variance_estimate} before computing $\vec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ using algorithm $\mathsf{CombEnc}$ elementwise and sending them back to the navigator. This is given by algorithm \ref{alg:measurement_info}.

    \item[Update] At each timestep $k$, the navigator aggregates and decrypts recieved measurement vectors and matrices with algorithm $\mathsf{AggDec}$, before computing the modified EIF update equations \eqref{eqn:eif_modified_vec_update} and \eqref{eqn:eif_modified_mat_update}. This is given by algorithm \ref{alg:nav_update}.
\end{LaTeXdescription}

\begin{algorithm}[htbp]
\caption{Navigator Prediction}\label{alg:nav_prediction}
\begin{algorithmic}[1]
    \Procedure{Prediction}{$\vec{x}_{k-1|k-1}$, $\mat{P}_{k-1|k-1}$, $\vec{f}$, $\mat{Q}$, $N$}

    \State Compute $\mat{F}_k$ by \eqref{eqn:jacobian_f}
    \State $\vec{x}_{k|k-1} \gets \vec{f}(\vec{x}_{k-1|k-1})$
    \State $\mat{P}_{k|k-1} \gets \mat{F}_k\mat{P}_{k-1|k-1}\mat{F}_k^\top + \mat{Q}_k$

    \State Compute $\mathsf{E}_{0}(x^3_{k|k-1})$ by \eqref{eqn:encode}
    \State Compute $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x^3_{k|k-1}))$ by \eqref{eqn:our_scheme_encrypt}
    \State Broadcast $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x^3_{k|k-1}))$ to sensors
    \For{Remaining weights in \eqref{eqn:weights_to_broadcast}} 
        \State Broadcast weight in the form above
    \EndFor

    \State \Return $\vec{x}_{k|k-1}, \mat{P}_{k|k-1}$
    \EndProcedure
\end{algorithmic}
\end{algorithm}

    \State Measure $z_{k,i}$
    \State Compute $z'_{k,i}$ by \eqref{eqn:modified_measurement}
    \State Compute $r_{k,i}$ by \eqref{eqn:modified_measurement_variance_estimate}

    \State Recieve $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x^3_{k|k-1}))$
    \For{Remaining weights in \eqref{eqn:weights_to_broadcast}}
        \State Recieve weight in the form above
    \EndFor

    \State Let $\alpha_{v}^{(i)}$ represent an encryption of element $v$ in $\vec{i}'_{k,i}$ from \eqref{eqn:hrz_linear_comb}
    \State $\alpha_{1}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(x^3_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{-1})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x_{k|k-1}y^2_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{-1})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x^2_{k|k-1}))^{\mathsf{E}_{0}(-r_{k, i}^{-1}s_{x,i})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(y^2_{k|k-1}))^{\mathsf{E}_{0}(-2r_{k, i}^{-1}s_{x,i})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{-1}z_{k,i}')}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x_{k|k-1}))^{\mathsf{E}_{0}(-2r_{k,i}^{-1}s_{x,i}^2)}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x_{k|k-1}))^{\mathsf{E}_{0}(-2r_{k,i}^{-1}s_{y,i}^2)}\cdot$\par
    \ $(N+1)^{\mathsf{E}_{1}(2r_{k,i}^{-1}s_{x,i}^3)}
    (N+1)^{\mathsf{E}_{1}(2r_{k,i}^{-1}s_{x,i}s_{y,i}^2)}\cdot$\par
    \ $(N+1)^{\mathsf{E}_{1}(-2r_{k, i}^{-1}s_{x,i}z_{k,i}')}
    H(k\mathbin\|1\mathbin\|1\mathbin\|0)\pmod{N^2}$
    \State Compute $\alpha_{2}^{(i)}$ using \eqref{eqn:hrz_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and remark \ref{rem:lcao_implicit_weight} in the form above
    \For{$v \gets 1$ to $2$}
        \State Send $\alpha_{v}^{(i)}$ to the navigator
    \EndFor

    \State Let $\beta_{vw}^{(i)}$ represent an encryption of element $(v,w)$ in $\mat{I}'_{k,i}$ from \eqref{eqn:hrh_linear_comb}
    \State $\beta_{11}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(x^2_{k|k-1}))^{\mathsf{E}_{0}(4r_{k,i}^{-1})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x_{k|k-1}))^{\mathsf{E}_{0}(-8r_{k, i}^{-1}s_{x,i})}\cdot$\par
    \ $(N+1)^{\mathsf{E}_{1}(4r_{k,i}^{-1}s_{x,i}^2)}\cdot$\par
    \ $H(k\mathbin\|1\mathbin\|1\mathbin\|1)\pmod{N^2}$
    \State Compute remaining $\beta_{vw}^{(i)}$ using \eqref{eqn:hrh_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and remark \ref{rem:lcao_implicit_weight} in the form above
    \For{$v \gets 1$ to $2$}
        \For{$w \gets 1$ to $2$} 
            \State Send $\beta_{vw}^{(i)}$ to the navigator
        \EndFor
    \EndFor
    \EndProcedure
\end{algorithmic}
\end{algorithm}

\begin{algorithm}[htbp]
\caption{Navigator Update}\label{alg:nav_update}
\begin{algorithmic}[1]
    \Procedure{Update}{$\vec{x}_{k|k-1}$, $\mat{P}_{k|k-1}$, $N$, $\lambda$}

    \State Let $\alpha_{v}$ represent an encryption of element $v$ in $\sum_{i=1}^n\vec{i}'_{k,i}$
    \For{$v \gets 1$ to $2$}
        \State $\alpha_{v} \gets \prod_{i=1}^n\alpha_{v}^{(i)}$
        \State Compute $\mathcal{D}_{sk_0}(\alpha_{v})$ with $\lambda$ by \eqref{eqn:our_scheme_decrypt}
        \State Compute $\mathsf{E}^{-1}_{1}(\mathcal{D}_{sk_0}(\alpha_{v}))$ by \eqref{eqn:decode}
    \EndFor
    \State Construct $\sum_{i=1}^n\vec{i}'_{k,i}$ from decoded decryptions above

    \State $\vec{y}_{k|k} \gets \mat{P}_{k|k-1}^{-1}\vec{x}_{k|k-1} + \sum_{i=1}^n\vec{i}'_{k,i}$
    \State $\mat{Y}_{k|k} \gets \mat{P}_{k|k-1}^{-1} + \sum_{i=1}^n\mat{I}'_{k,i}$
    \State $\vec{x}_{k|k} \gets \mat{Y}_{k|k}^{-1}\vec{y}_{k|k}$
    \State $\mat{P}_{k|k} \gets \mat{Y}_{k|k}^{-1}$
    \State \Return $\vec{x}_{k|k}, \mat{P}_{k|k}$
    \EndProcedure
\end{algorithmic}
\end{algorithm}

Algorithms \ref{alg:nav_prediction}, \ref{alg:measurement_info} and \ref{alg:nav_update} have also been summarised graphically in figure \ref{fig:alg_steps}. Here, for brevity, $\mathcal{E}_{pk_0,sk_i}(\cdot)$ and $\mathsf{E}_d(\cdot)$ denote elementwise operations with the same parameters.
\begin{figure}[htbp]
\centering
\begin{tikzpicture}[font=\footnotesize,scale=0.95]
    % Prediction
    \draw [gray] (0,2) rectangle (6.5,8);
    \node at (3.25,7.5) {\small 1. Prediction};

    % Navigator
    \fill  [blue!40] (2,7) rectangle (4.5,5.5);
    \pic[xscale=0.22,yscale=0.3] at (3.25,6.6725) {plane};
    \node at (3.25,5.875) {$\vec{x}_{k|k-1}$, $\mat{P}_{k|k-1}$};

    \fill [lightgray]  (0.25,5) rectangle (6.25,4);
    \node at (3.25,4.5) {$\left\{\mathcal{E}_{pk_0}(\mathsf{E}_0(\rv{\omega})) \,|\, \rv{\omega} \!\in\! \{\rv{x}^3_{k|k-1}, \rv{y}^3_{k|k-1}, \dots\}\right\}$};

    \node at (1.25,-3.125) {$z'_{k,1}$, $r_{k,1}$};
    \node at (5.25,-3.125) {$z'_{k,n}$, $r_{k,n}$};

    \fill [lightgray]  (0.375,-0.875) rectangle (3.125,-1.875);
    \node[align=center] at (1.75,-1.375) {$\mathcal{E}_{pk_0,sk_1}(\mathsf{E}_1(\vec{i}'_{k,1}))$,\\$\mathcal{E}_{pk_0,sk_1}(\mathsf{E}_1(\mat{I}'_{k,1}))$};
    \fill [lightgray]  (3.375,-0.875) rectangle (6.125,-1.875);
    \node[align=center] at (4.75,-1.375) {$\mathcal{E}_{pk_0,sk_n}(\mathsf{E}_1(\vec{i}'_{k,n}))$,\\$\mathcal{E}_{pk_0,sk_n}(\mathsf{E}_1(\mat{I}'_{k,n}))$};

    % Navigator
    \fill  [blue!40] (1.5,-5.5) rectangle (5,-7.5);
    \pic[xscale=0.22,yscale=0.3] at (3.25,-5.8275) {plane};
    \node at (3.25,-6.625) {$\sum_{i=1}^n \vec{i}'_{k,i}$, $\sum_{i=1}^n\mat{I}'_{k,i}$};
    \node at (3.25,-7.125) {$\vec{x}_{k|k}$, $\mat{P}_{k|k}$};
\end{tikzpicture}
\caption{Procedure at timestep $k$ for the proposed privacy-preserving EIF.}
\label{fig:alg_steps}
\end{figure}

@@
